Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
Move the subsection 3.1, 3.2 and 3.3 into their own section, 3, 4 and 5.

\section{Method}

\cfbolz{this needs a better section title. "Transactional Memory Implementation"?}

We now take a closer look at how our TM system that we use to replace
the GIL works, what properties it has, and how it is implemented.

\subsection{Transactional Memory Model}

@@

\subsubsection{Conflict Handling}

@@

\subsubsection{Semantics}

@@

\subsection{Implementation}

@@

\subsubsection{Memory Segmentation and Page Sharing}

@@

\subsubsection{Memory Segmentation on the x86}

@@

\subsubsection{Conflict detection}

@@

\subsection{Low-level Implementation\label{sub:Low-level-Implementation}}

@@

\subsubsection{Architecture}

@@

\subsubsection{Application Programming Interface\label{sub:Application-Programming-Interfac}}

@@

\subsubsection{Setup\label{sub:Setup}}

@@

\subsubsection{Assigning Segments}

@@

\subsubsection{Garbage Collection}

@@

\subsubsection{Read Barrier}

@@

\subsubsection{Write Barrier}

@@

\subsubsection{Abort}

@@

\subsubsection{Commit}

@@

\subsubsection{Thread Synchronisation}

@@

\subsubsection{Contention Management\label{subsub:contentionmanagement}}

>>>>

\section{Transactional Memory Model}

@@

\subsection{Conflict Handling}

@@

\subsection{Semantics}

@@

\section{High-level overview}

@@

\subsection{Memory Segmentation and Page Sharing}

@@

\subsection{Memory Segmentation on the x86}

@@

\subsection{Conflict detection}

@@

\section{Low-level Implementation\label{sub:Low-level-Implementation}}

@@

\subsection{Architecture}

@@

\subsection{Application Programming Interface\label{sub:Application-Programming-Interfac}}

@@

\subsection{Setup\label{sub:Setup}}

@@

\subsection{Assigning Segments}

@@

\subsection{Garbage Collection}

@@

\subsection{Read Barrier}

@@

\subsection{Write Barrier}

@@

\subsection{Abort}

@@

\subsection{Commit}

@@

\subsection{Thread Synchronisation}

@@

\subsection{Contention Management\label{subsub:contentionmanagement}}
